---
title: "p8105_hw1_fw2334"
author: "Frances Williams"
date: "9/18/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Problem 1

```{r}
problem1_df = tibble(
  sample1 = rnorm(8),
  vec_logical = sample1 > 0,
  vec_char = c("Ex1", "Ex2", "Ex3", "Ex4", "Ex5", "Ex6", "Ex7", "Ex8"),
  vec_factor = factor(c("Level1", "Level2", "Level3", "Level1", "Level2", "Level3", "Level1", "Level2"))
)

mean(pull(problem1_df, sample1))
mean(pull(problem1_df, vec_logical))
mean(pull(problem1_df, vec_char))
mean(pull(problem1_df, vec_factor))

```

The character and factor vectors don't have means, and return an "NA" message.

```{r}
vec_log_num = as.numeric(pull(problem1_df, vec_logical))
vec_char_num = as.numeric(pull(problem1_df, vec_char))
vec_factor_num = as.numeric(pull(problem1_df, vec_factor))
```

```{r}
mutate(problem1_df,
       log_numxnorm = as.numeric(pull(problem1_df, vec_logical)) * sample1,
       log_factorxnorm = as.factor(pull(problem1_df, vec_logical)) * sample1,
       log_fact_numxnorm = as.numeric(as.factor(pull(problem1_df, vec_logical))) * sample1
       )

```

# Problem 2

```{r}
set.seed(1234)
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical2 = (x + y) > 1,
  vec_num2 = as.numeric(vec_logical2),
  vec_factor2 = as.factor(vec_logical2)
)
```

### Description of dataset
The dataset has `r nrow(problem2_df)` rows and `r ncol(problem2_df)` columns.
The mean of `x` is `r mean(pull(problem2_df, x))`.
The median of `x` is `r median(pull(problem2_df, x))`.
The standard deviation of `x` is `r sd(pull(problem2_df, x))`.
The proportion of cases for when `x+y` is greater than 1 is `r mean(problem2_df$vec_logical2 == TRUE)`.

### Scatterplots
```{r}
xy_scatter = ggplot(problem2_df, aes(x = x, y = y, color = vec_logical2)) + geom_point()
xy_scatter

ggplot(problem2_df, aes(x = x, y = y, color = vec_num2)) + geom_point()

ggplot(problem2_df, aes(x = x, y = y, color = vec_factor2)) + geom_point()

ggsave('scatterplot.png', plot = xy_scatter)
```



