---
title: "p8105_hw1_fw2334"
author: "Frances Williams"
date: "9/18/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Problem 1

#### Dataframe creation and variable means
```{r}
set.seed(1234)
problem1_df = tibble(
  sample1 = rnorm(8),
  vec_logical = sample1 > 0,
  vec_char = c("Ex1", "Ex2", "Ex3", "Ex4", "Ex5", "Ex6", "Ex7", "Ex8"),
  vec_factor = factor(c("Lvl1", "Lvll2", "Lvl3", "Lvl1", "Lvl2", "Lvl3", "Lvl1", "Lvl2"))
)

mean(pull(problem1_df, sample1))
mean(pull(problem1_df, vec_logical))
mean(pull(problem1_df, vec_char))
mean(pull(problem1_df, vec_factor))
```

We are able to take the mean of the normal sample and the logical vector, but not the character and factor vectors.

#### Numeric conversions
```{r eval = FALSE}
as.numeric(pull(problem1_df, vec_logical))
as.numeric(pull(problem1_df, vec_char))
as.numeric(pull(problem1_df, vec_factor))
```
The conversion of the character vector returns NAs by coercion because a character vector cannot be converted to numeric. This explains why we cannot take the mean of the charcter vector. 
We can, however, convert the factor variable: since it is categorical, R can assign each category a numeric value. While we were unable to take the mean of the factor when the categories were text, now we would be able to. 

#### Logical vector conversions
```{r}
as.numeric(pull(problem1_df, vec_logical)) * pull(problem1_df, sample1)
as.factor(pull(problem1_df, vec_logical)) * pull(problem1_df, sample1)
as.numeric(as.factor(pull(problem1_df, vec_logical))) * pull(problem1_df, sample1)
```
Reinforcing our findings above, when we convert the logical vector to a factor, we cannot multiply it by anything without first converting it to numeric.

# Problem 2

#### Dataframe creation
```{r}
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical2 = (x + y) > 1,
  vec_num2 = as.numeric(vec_logical2),
  vec_factor2 = as.factor(vec_logical2)
)
```

#### Description of dataset
* The dataset has `r nrow(problem2_df)` rows and `r ncol(problem2_df)` columns.
* The mean of `x` is `r mean(pull(problem2_df, x))`.
* The median of `x` is `r median(pull(problem2_df, x))`.
* The standard deviation of `x` is `r sd(pull(problem2_df, x))`.
* The proportion of cases for when `x+y` is greater than 1 is `r sum(pull(problem2_df, vec_logical2))/nrow(problem2_df)`.

#### Scatterplots
```{r}
xy_scatter = ggplot(problem2_df, aes(x = x, y = y, color = vec_logical2)) + geom_point()
xy_scatter

ggplot(problem2_df, aes(x = x, y = y, color = vec_num2)) + geom_point()

ggplot(problem2_df, aes(x = x, y = y, color = vec_factor2)) + geom_point()

ggsave('scatterplot.png', plot = xy_scatter)
```



